---
title: "Weight of Fish"
author: "Your Name"
date: "Year 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(readr)
Fish <- read_csv("Fish.csv") 
  Species <- as.factor(Fish$Species)
Perch <- subset(Fish,Species=="Perch")
  Perch <- select(Perch, -Species)
Bream <- subset(Fish,Species=="Bream")
  Bream <- select(Bream, -Species)
Smelt <- subset(Fish,Species=="Smelt")
  Smelt <- select(Smelt, -Species)
```

# Perch model. 
<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
According to the automation, the best 2 variables for predicting Weight are Height and Width.  
```{r}
which.max(summary.out$adjr2)
```
  The model with those 2 variables has the greatest Adjusted R-squared, meaning it explains the greatest percentage of the data in Perch.  
```{r}
best.model <- lm(Weight~ Height + Width,data=Perch)
summary(best.model)
```
## Results
## Inferential Results.

# Bream model.  
```{r}

```
## Results
## Inferential Results.

# Smelt model. 
## Results
## Inferential Results.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
